A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}\censornotice

### 2020-01-25 0_reviewer_response.tex

\stepcounter{question}
\subQue{
The authors should highlight their contributions compared to the existing approaches for generating toolpaths with adaptive width.
}\label{contributions}
\Ans{
The contributions were already listed at the end of the introduction, but now we highlight them in comparison to existing techniques.
The focus on the comparison to existing techniques has also been applied to the conclusion.
See also our response to question~\ref{difference_to_jin}.
}
\commits{
66d006d91d406c0064ee1f4f1e4df85fc0821994 % new contributions enumeration
e806d40e5e6d2bbe450c6792b802f0fcce4df645 % lil typo
86c5aa8fab91e326e658f79a0746462fb99ea2b0 % changes to conclusion
}
\paper{Intro}
{
In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill
\revise{}{and introduce a beading scheme which reduces the bead width variation compared to the state of the art.} 
We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
\revise{
For FDM printing in particular we propose a novel scheme which reduces the amount of over- and underfill while ensuring the extrusion beads deviate little from the nozzle size.
}{Furthermore we present an approach to accurately realize adaptive bead width.
}
See \cref{intro_wedge_distributed}. 
% In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
% Some such toolpath generation techniques have already been developed.

Our contributions are as follows:
\begin{itemize}
\item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
\item A specific beading scheme for FDM printing which
\revise{}{furthermore} reduces the amount of \revise{deviation}{variation} in the extrusion widths compared to \revise{existing literature, }{the state of the art to be below a factor of 2.}
\revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}
\revise{}{
\item A back pressure compensation approach to accurately realize adaptive bead width on Bowden style hardware systems.
}
\end{itemize}
}
\paper{Conclusion}{
In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize \revise{underfilland}{underfill and} overfill areas\revise{.}{,
we introduced beading schemes which improve on the state of the art
and we have introduced a backpressure compensation method for accurate fabrication of adaptive width.
}

@@

\paper{4. Beading schemes, end of section}{
\paragraph{Widening \revise{}{meta-scheme}}
Complementary to any of these schemes we can enforce a minimum feature size \revise{at no extra cost}{and minimum bead width} in our framework.
Regions where the model is narrower than \revise{the nozzle size}{some $r_\text{min}$} can be printed with a bead width \revise{}{$w_\text{min}$} larger than the model thickness.
See \cref{min_feature_size} and~\subref{widening}.
We can simply override
\begin{align*}
q'(d) &= 
\begin{cases}
0 & \text{ if } 0 \leq d < 2 r_\text{min} \\
1 & \text{ if }  2 r_\text{min} \leq d < w^*  \\
q(d) & \text{ otherwise}
\end{cases}
\\
W'(n,r)_0 &=
\begin{cases}
\max \left( w_\text{min}  ,  2 r \right) & \text{ if } 2 r < w^* \\
W(n,r)_0 & \text{ otherwise}
\end{cases}
\end{align*}

\revise{}{
\paragraph{Shell meta-scheme}
The industry standard of FDM is to generate only a limited contour-parallel perimeters and to fill the remainder using a direction-parallel strategy.
We therefore provide a meta-scheme to generate adaptive bead width toolpaths only in narrow regions and generate the limited number of perimeters $M$ using the preferred width in regions which are wide enough.
We also take care not to leave gaps which are too small to be filled using the direction-parallel strategy:
}

\revise{}{
\begin{align*}
q'(d) &= \min(M, q(d))
\\
W'(n,r)_i &= 
\begin{cases}
W(n, M w^*)_i & \text{ if } 2 r > q^{-1}(M) \\
W(n,r)_i & \text{ otherwise}
\end{cases}
\end{align*}
}

\revise{}{
These meta-schemes introduce non-linearities in the quantization function.
Because the beading is only evaluated at nodes in the skeleton, we need to make sure that there are nodes at the locations along the skeleton where the non-linearities happen.
We therefore insert extra nodes along with their ribs at locations $v$ with a radial distance $R(v) = r_\text{min}$ for widening and at $R(v) \in \left\{ M w^*, q^{-1}(M), q^{-1}(M) + \nicefrac12 w^* \right\} $ for the transition from narrow shell to unconstrained shell.
Combining all meta-schemes functionality we can generate results such as depicted in \cref{shell}.
}
\begin{figure}
\centering
\setlength{\figwidth}{.35\mycolumnwidth}
\setlength{\figwidthTwo}{.6\mycolumnwidth}
\begin{minipage}[b]{\figwidthTwo} \centering
\begin{subfigure}[b]{\figwidthTwo}\centering
\includegraphics[width=\figwidthTwo]{sources-validation-wedge-TEST-Distributed-feature-size.png}
\caption{Widening meta-scheme using $w_\text{min} = 2 r_\text{min} = 0.1$
\\ on top of the Distributed scheme}
\label{min_feature_size}
\end{subfigure}
\begin{subfigure}[b]{\figwidthTwo}\centering
\includegraphics[width=\figwidthTwo]{sources-validation-wedge-TEST-Center-widening.png}
\caption{Widening meta-scheme using $w_\text{min} = 0.5$, $2 r_\text{min} = 0.2$ 
\\ on top of the Center scheme}
\label{widening}
\end{subfigure}
\end{minipage}
\begin{subfigure}[b]{\figwidth}\centering
\includegraphics[width=\figwidth]{sources-validation-gMat_example_all_combined.png}
\caption{Shell and widening}
\label{shell}
\end{subfigure}
\caption{
Toolpaths using the widening and shell meta-schemes.
\subref{min_feature_size} and~\subref{widening} show widening.
\subref{shell}
show toolpaths generated with the inward distributed strategy ($N=1.5$) in conjunction with the shell meta-scheme ($M=4$) and the same widening as in~\subref{widening}.
% -p test_geometry/gMAT_example.svg -b 4 -s i -n 1.5 -a --mins 0.2 --minw .5
Widening and shell require extra edges (green) at key locations in the skeleton.
The azure area is to be filled using some direction-parallel toolpaths.
}
\label{widening_shell}
\end{figure}
}
\paper{5.2 Computational results}
{
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library,
and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using \revise{$N=3$}{$N=2$}, all with a preferred bead width\revise{s}{} of \revise{$w^* = \SI{0.4}{\milli\meter}$}{$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
}

@@

Figure~\ref{no_corners} shows an example of a shape without sharp corners, and which also requires a large bead width variation when using the constant bead count approach by Ding et al.
}
\begin{figure} \centering
\setlength{\figwidth}{.45\mycolumnwidth}
\begin{subfigure}[b]{\figwidth} \centering
\includegraphics[rotate=-90,width=\linewidth]{response_rects_Center_accuracy.png}
\caption{Problematic for center, i.e. Jin et al 2017 JMS, exhibiting $4.5w^*$ and $5.8w^*$}
\end{subfigure}
\begin{subfigure}[b]{\figwidth} \centering
\includegraphics[width=\linewidth]{response_no_corners}
\caption{Problematic for constant, i.e. Ding et al}
\end{subfigure}
\caption{Example shapes without sharp corners.}
\label{no_corners}
\end{figure}

\Que{
How do the authors conduct path planning? Could the authors add a simple 2D geometry with multiple holes to explain the path planning process? As the proposed approach adds more disconnected toolpaths to minimize underfill areas, an improper path planning would significantly increase the fabrication time. 
}
\Ans{
We now included a description of the path order algorithm, which is naive and greedy.
Although an optimal path order algorithm might influence the travel time, such an algorithm is slow and not generally used in the industry.
The software package Cura currently employs a similarly greedy algorithm.
Travel times are approximately \SI{2}{\percent} of the total print time in our current setup, so the effect of improper path planning is negligible compared to the differences in extrusion time.

We now include statistics on extrusion time, travel time and path counts.
These new statistics are now also reflected upon in the comparison of the beading schemes.

Because the extrusion time depends on the actual printing setup we have moved the section on print results to before the statistics section.
}
\commits{
d375878a8a6d01c53436aeb9c473dbedd8f3edcf % path order algorithm
e2c940f2362556ae8d017cff63c81b4bbcb77286 % print time, path count statistics
7f567012b409445fc120968e995f861cab56e776 % new beading schemes comparison
bf403fe797193e40b004c2cae806935f699271e5 % move print results to before statistics 
b106dd1e0067114756bf96a7dc10458202380f2e % new print time pdf graph
}
\paper{5.1.2 Print results}{\revise{}{The printing order is determined greedily by choosing the closest point of a polygonal extrusion path, or the closest of either end point in case of an open polyline extrusion path.}} 
\paper{5.2.3 Print time}
{
\revisepar{
\subsubsection{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We therefore measured the angle between consecutive extrusion segments generated by each scheme
and report on the occurrence of each angle in \cref{smoothness}.
All schemes show a higher number of corners for smaller angles with a peak towards \SI{180}{\degree} (straight).
We observe that compared to the uniform method our framework produces less acute angles which, but more obtuse angles.
The inward distributed scheme produces an order of magnitude less corners around \SI{150}{\degree}, compared to evenly distributed. 
We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}. 
}{
\subsubsection{Print time}
The total time it takes to print a part is influenced not only by our back pressure compensation scheme, but also by the geometry of the toolpaths.
In order to separate these effects we report on the total print time when using back pressure compensation and when using a constant (maximum) movement speed in \cref{printtime}.
We estimate print times using a simulation of the Marlin firmware using the default movement settings of the setup described in \cref{print_results_section}.
While the idealized print time is predominantly determined by the total toolpath length, the print time using back pressure compensation is predominantly determined by the occurrence of wide beads, because they have a reduced the flow in \si{\milli\meter\cubed\per\second}.
Because of acceleration constraints imposed by the hardware the maximum movement speed is not reached near sharp corners.
We therefore also report on the angles of the bends in the toolpaths in \cref{smoothness}.
Furthermore, the print time is negatively affected by discontinuities in the extrusion process.
Between extrusions the printer needs to stop extrusion, travel to the next extrusion path and restart the extrusion process, which all take time.
For closed polygonal toolpaths we can start anywhere within the path, so we can optimize the starting location so as to minimize the travel time.
We therefore report both on the open and closed path count in \cref{pathcounts}.
}
}
\paper{5.3 Comparison of beading schemes}
{
We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average \revise{approximately}{} \revise{\SI{1}{\percent}}{\SI{1.6}{\percent}} of the total target area is covered by underfill and likewise for overfill.
To our knowledge, the uniform beading scheme, as well as the outer beading scheme, is of little use to FDM printers.

The constant bead count scheme effectively deals with underfills, but generates orders of magnitude more overfills compared to the other schemes. 
Also, the scheme comes at the cost of greatly varying bead widths and an average bead width that is not close to the preferred bead width.
Note that most overfill areas occur near regions of alternating bead width. 
\revise{}{While the scheme results in short toolpaths, as indicated by the idealized print time, it also results in a wide range of bead widths, which cause the back pressure compensation print time to be very large.
See \cref{statisticsfig}.}
For an input outline shape which contains both very small and very large features, the constant bead count scheme produces bead widths which can fall outside of the range of manufacturable bead widths.
Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.
\revise{}{See top right of \cref{TEST_Constant_accuracy}.}

In \cref{TEST_Center_accuracy} we can see that
the centered beading scheme effectively deals with \revise{both }{}overfill \revise{and underfill }{}and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e. the variation is within a factor of $3.6$.}
\revise{}{However, it does produce some narrow underfill regions.}
\revise{
According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.
}{
Compared to the uniform technique the centered technique increases the (open) path count, but considerably reduces over- and underfill and decimates the number of toolpath angles below \SI{45}{\degree}.
See \cref{statisticsfig}.
}

@@

\end{definition}
}{}

\revisepar{
The following restrictions hold:
\begin{enumerate}
	\begin{minipage}{\mycolumnwidth}
	\setlength\intextsep{0pt}
	\begin{wrapfigure}[4]{o}{.4\mycolumnwidth} %\centering
	\includegraphics[width=.3\mycolumnwidth,frame]{sources-method-transition-length-limit.pdf}
	%\caption{
	%%Transition ends (magenta and pink) shouldn't cross each other.
	%Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a ST edge (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
	%The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
	%}
	\label{transition_placement}
	\end{wrapfigure}
	\item Transitions shouldn't overlap each other: \\ $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ \\ for each $n \in \mathbb{N}$ \\ (see \cref{transition_placement})
\end{minipage}
\item An odd beading should produce an odd single toolpath exactly in the center: $B(n, r)_{\lfloor n/2 \rfloor} = r$ in case $n$ is odd
\item For the smoothness and continuity of toolpaths we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$
\end{enumerate}
}{}

\revise{}{
\begin{definition}\label{beading_scheme_definition}
A beading scheme is defined by the quantization operator $q$ and the beading operator $B$: $\{q(d), B(n ,r)\}$.
The beading function $B(n,r)$ consists of $\left( W(n,r), L(n,r) \right)$,
which provides sequences of $n$ bead widths and of $n$ distances from the outline to fill up a radial distance $r$.
\end{definition}
}
% the condition that transitions don't overlap is already caught by the way in which we defined $t_0$ in section 3.4 Smooth transitions

@@

We fixed a mistake when performing the statistical analysis. In the first submitted version we used a minimum bead width half of what it should have been for the centered scheme. The extrusion width statistics figure (19d) now shows little beads below \SI{0.2}{\milli\meter} instead of below \SI{0.1}{\milli\meter}.

Explain why and how statistics are gathered over the whole data set:
\commits{17135b010f5ac51fda77357136a19f67a80dbc33}
\paper{5.2 Computational results}
{
\revise{}{We report on the total statistics summed over the whole data set, because averaging would be biased.}
}

Remove wrapfigure explaining the area covered by a single extrusion move (in section 5.2.1 `Accuracy'), since that is already explained in the appendix.
\commits{d402ba3a47d35bc9a040b6ed4ccdfb85e911bedf}

Change width histogram calculation so that we use accurate statistics instead of sampling the width along the path:
\commits{d402ba3a47d35bc9a040b6ed4ccdfb85e911bedf}
\paper{5.2.2 Uniformity}
{
\revise{
We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
}{
We binned the toolpaths into width bins at \SI{0.01}{\milli\meter} increments and determine the total toolpath length pertaining to each bin.
From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.
}
}

### 2020-01-25 12_conclusions_future_work.tex
spell check

\section{Conclusion and future work}
In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfilland overfill areas\revise{.}{,
we introduced beading schemes which improve on the state of the art
and we have introduced a backpressure compensation method for accurate fabrication of adaptive width.
}

>>>>

\section{Conclusion and future work}
In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas\revise{.}{,
we introduced beading schemes which improve on the state of the art
and we have introduced a back pressure compensation method for accurate fabrication of adaptive width.
}

### 2020-01-25 1_intro.tex
spell check

\begin{figure}\centering
\setlength{\figwidth}{.9\columnwidth}
\setlength{\figwidthTwo}{.05\columnwidth}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths.png}
\end{subfigure}
\caption{
Illustration of different toolpath\revise{}{s} for a \revise{wedge }{}shape \revise{}{showcasing a range of shape radii }\revise{}{(black)}.
\revise{}{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
\subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicatd in red and blue, respectively.
\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
}
\label{intro_wedge}
\end{figure}

>>>>

\begin{figure}\centering
\setlength{\figwidth}{.9\columnwidth}
\setlength{\figwidthTwo}{.05\columnwidth}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths.png}
\end{subfigure}
\caption{
Illustration of different toolpath\revise{}{s} for a \revise{wedge }{}shape \revise{}{showcasing a range of shape radii }\revise{}{(black)}.
\revise{}{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
\subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are \revise{indicatd}{indicated} in red and blue, respectively.
\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
}
\label{intro_wedge}
\end{figure}

### 2020-01-25 4_method.tex
fix typo
spell check

%\subsubsection{Medial axis transform}
\paragraph{Medial axis transform}
The medial axis is a \revise{compact and complete representation of}{representation commonly used to analyse} a shape.
It is defined as the set of positions where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation,lee1982medial}.
The resulting skeleton consists of straight edges and parabolic edges.
An example is illustrated in \cref{shape_decomposition_mat}.
We call the set of points on the outline polygon $P$ closest to a skeletal point $v$ its \emph{support}:
\begin{equation}
    \text{sup}(v) = \argmin_{x\in P} |x - v|.
\end{equation}
The shortest distance for a point on the skeleton is called its feature radius, $R(v)$.
%See \cref{MAT_explanation_circles}.
%We therefore represent the skeleton in a standard half-edge data-structure.
%See \cref{shape_decomposition_datastructure}.
%Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous~\cite{blum1967transformation}
%The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
%See \cref{MAT_explanation}.
The medial axis along with the feature radius values along the skeleton form a complete shape descriptor, known as the medial axis transform (MAT).
%Feature radius and node locations will be used below to analyse the shape locally.

@@

\subsection{Center classification}\label{sec_center_classification}
%The simple technique of performing uniform width offset produces large overfill and underfill areas on central regions of the ST.
%These central regions present themselves as upper ridges in the mountains of the UoC surface.
%In order to prevent the over- and underfill we will change the bead counts in the central regions.
%This sections covers what parts of the UoC will be marked as being central.
In order to prevent over- and underfill to occur in central, we mark parts of the ST as being central.
\revise{The remainder is called peripheral.}{}
Our framework will decide on a beading at all the marked nodes in `the center' and apply the beading outward to the unmarked nodes (\cref{sec_peripheral_height_adjustment}).

>>>>

%\subsubsection{Medial axis transform}
\paragraph{Medial axis transform}
The medial axis is a \revise{compact and complete representation of}{representation commonly used to analyze} a shape.
It is defined as the set of positions where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation,lee1982medial}.
The resulting skeleton consists of straight edges and parabolic edges.
An example is illustrated in \cref{shape_decomposition_mat}.
We call the set of points on the outline polygon $P$ closest to a skeletal point $v$ its \emph{support}:
\begin{equation}
    \text{sup}(v) = \argmin_{x\in P} |x - v|.
\end{equation}
The shortest distance for a point on the skeleton is called its feature radius, $R(v)$.
%See \cref{MAT_explanation_circles}.
%We therefore represent the skeleton in a standard half-edge data-structure.
%See \cref{shape_decomposition_datastructure}.
%Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous~\cite{blum1967transformation}
%The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
%See \cref{MAT_explanation}.
The medial axis along with the feature radius values along the skeleton form a complete shape descriptor, known as the medial axis transform (MAT).
%Feature radius and node locations will be used below to analyse the shape locally.

@@

\subsection{Center classification}\label{sec_center_classification}
%The simple technique of performing uniform width offset produces large overfill and underfill areas on central regions of the ST.
%These central regions present themselves as upper ridges in the mountains of the UoC surface.
%In order to prevent the over- and underfill we will change the bead counts in the central regions.
%This sections covers what parts of the UoC will be marked as being central.
In order to prevent over- and underfill \revise{to occur}{from occurring} in central\revise{}{ regions}, we mark parts of the ST as being central.
\revise{The remainder is called peripheral.}{}
Our framework will decide on a beading at all the marked nodes in `the center' and apply the beading outward to the unmarked nodes (\cref{sec_peripheral_height_adjustment}).

### 2020-01-25 5_generalization.tex
lil typo fixes
spell check

\revise{}{
\begin{definition}\label{beading_scheme_definition}
A beading scheme is defined by the quatization operator $q$ and the beading operator $B$: $\{q(d), B(n ,r)\}$.
The beading function $B(n,r)$ consists of $\left( W(n,r), L(n,r) \right)$,
which provides sequences of $n$ bead widths and of $n$ distances from the outline to fill up a radial distance $r$.
\end{definition}
}

@@

\paragraph{Uniform beading scheme}
We can define a beading scheme which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
\revise{See}{We can simply set $\alpha_\text{max} = \SI{180}{\degree}$ and supply a simply beading scheme given by} \cref{formula_uniform}.

@@

\begin{figure}
\centering
\setlength{\figwidth}{.35\columnwidth}
\setlength{\figwidthTwo}{.6\columnwidth}
\begin{minipage}[b]{\figwidthTwo} \centering
\begin{subfigure}[b]{\figwidthTwo}\centering
\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Distributed-feature-size.png}
\caption{Widening meta-scheme using $w_\text{min} = 2 r_\text{min} = 0.1$
\\ on top of the Distributed scheme}
\label{min_feature_size}
\end{subfigure}
\begin{subfigure}[b]{\figwidthTwo}\centering
\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Center-widening.png}
\caption{Widening meta-scheme using $w_\text{min} = 0.5$, $2 r_\text{min} = 0.2$ 
\\ on top of the Center scheme}
\label{widening}
\end{subfigure}
\end{minipage}
\begin{subfigure}[b]{\figwidth}\centering
\includegraphics[width=\figwidth]{sources-validation-gMat_example_all_combined.png}
\caption{Shell and widening}
\label{shell}
\end{subfigure}
\caption{
Toolpaths using the widening and shel meta-schemes.
\subref{min_feature_size} and~\subref{widening} show widening.
\subref{shell}
show toolpaths generated with the inward distributed strategy ($N=1.5$) in conjunction with the shell meta-scheme ($M=4$) and the same widening as in~\subref{widening}.
% -p test_geometry/gMAT_example.svg -b 4 -s i -n 1.5 -a --mins 0.2 --minw .5
Widening and shell require extra edges (green) at key locations in the skeleton.
The azure area is to be filled using some direction-parallel toolpaths.
}
\label{widening_shell}
\end{figure}

>>>>

\revise{}{
\begin{definition}\label{beading_scheme_definition}
A beading scheme is defined by the quantization operator $q$ and the beading operator $B$: $\{q(d), B(n ,r)\}$.
The beading function $B(n,r)$ consists of $\left( W(n,r), L(n,r) \right)$,
which provides sequences of $n$ bead widths and of $n$ distances from the outline to fill up a radial distance $r$.
\end{definition}
}

@@

\paragraph{Uniform beading scheme}
We can define a beading scheme which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
\revise{See}{We can simply set $\alpha_\text{max} = \SI{180}{\degree}$ and supply a simple beading scheme given by} \cref{formula_uniform}.

@@

\begin{figure}
\centering
\setlength{\figwidth}{.35\columnwidth}
\setlength{\figwidthTwo}{.6\columnwidth}
\begin{minipage}[b]{\figwidthTwo} \centering
\begin{subfigure}[b]{\figwidthTwo}\centering
\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Distributed-feature-size.png}
\caption{Widening meta-scheme using $w_\text{min} = 2 r_\text{min} = 0.1$
\\ on top of the Distributed scheme}
\label{min_feature_size}
\end{subfigure}
\begin{subfigure}[b]{\figwidthTwo}\centering
\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Center-widening.png}
\caption{Widening meta-scheme using $w_\text{min} = 0.5$, $2 r_\text{min} = 0.2$ 
\\ on top of the Center scheme}
\label{widening}
\end{subfigure}
\end{minipage}
\begin{subfigure}[b]{\figwidth}\centering
\includegraphics[width=\figwidth]{sources-validation-gMat_example_all_combined.png}
\caption{Shell and widening}
\label{shell}
\end{subfigure}
\caption{
Toolpaths using the widening and shell meta-schemes.
\subref{min_feature_size} and~\subref{widening} show widening.
\subref{shell}
show toolpaths generated with the inward distributed strategy ($N=1.5$) in conjunction with the shell meta-scheme ($M=4$) and the same widening as in~\subref{widening}.
% -p test_geometry/gMAT_example.svg -b 4 -s i -n 1.5 -a --mins 0.2 --minw .5
Widening and shell require extra edges (green) at key locations in the skeleton.
The azure area is to be filled using some direction-parallel toolpaths.
}
\label{widening_shell}
\end{figure}

### 2020-01-25 6_validation.tex
spell check

\subsubsection{Uniformity}
We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.
\revise{
We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
}{
We binned the tool paths into width bins at \SI{0.01}{\milli\meter} increments and determine the total tool path length pertaining to each bin.
From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.
}
We found that the mean width of the inward and evenly distributed schemes is close to preferred bead width of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme. 
These results show that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.
\revise{
We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
The outer beads of the inward distributed scheme deviate less from the preferred width compared to the evenly distributed scheme.
}{}

\revise{
\subsubsection{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We therefore measured the angle between consecutive extrusion segments generated by each scheme
and report on the occurrence of each angle in \cref{smoothness}.
All schemes show a higher number of corners for smaller angles with a peak towards \SI{180}{\degree} (straight).
We observe that compared to the uniform method our framework produces less acute angles which, but more obtuse angles.
The inward distributed scheme produces an order of magnitude less corners around \SI{150}{\degree}, compared to evenly distributed. 
We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}. 
}{
\subsubsection{Print time}
The total time it takes to print a part is influenced not only by our back pressure compensation scheme, but also by the geometry of the tool paths.
In order to separate these effects we report on the total print time when using back pressure compensation and when using a constant (maximum) movement speed in \cref{printtime}.
We estimate print times using a simulation of the Marlin firmware using the default movement settings of the setup described in \cref{print_results_section}.
While the idealized print time is predominantly determined by the total tool path length, the print time using back pressure compensation is predominantly determined by the occurrence of wide beads, because they have a reduced the flow in \si{\milli\meter\cubed\per\second}.
Because of acceleration constraints imposed by the hardware the maximum movement speed is not reached near sharp corners.
We therefore also report on the angles of the bends in the toolpaths in \cref{smoothness}.
Furthermore, the print time is negatively affected by discontinuities in the extrusion process.
Between extrusions the printer needs to stop extrusion, travel to the next extrusion path and restart the extrusion process, which all take time.
For closed polygonal tool paths we can start anywhere within the path, so we can optimize the starting location so as to minimize the travel time.
We therefore report both on the open and closed path count in \cref{pathcounts}.
}

>>>>

\subsubsection{Uniformity}
We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.
\revise{
We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
}{
We binned the toolpaths into width bins at \SI{0.01}{\milli\meter} increments and determine the total toolpath length pertaining to each bin.
From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.
}
We found that the mean width of the inward and evenly distributed schemes is close to preferred bead width of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme. 
These results show that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.
\revise{
We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
The outer beads of the inward distributed scheme deviate less from the preferred width compared to the evenly distributed scheme.
}{}

\revise{
\subsubsection{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We therefore measured the angle between consecutive extrusion segments generated by each scheme
and report on the occurrence of each angle in \cref{smoothness}.
All schemes show a higher number of corners for smaller angles with a peak towards \SI{180}{\degree} (straight).
We observe that compared to the uniform method our framework produces less acute angles which, but more obtuse angles.
The inward distributed scheme produces an order of magnitude less corners around \SI{150}{\degree}, compared to evenly distributed. 
We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}. 
}{
\subsubsection{Print time}
The total time it takes to print a part is influenced not only by our back pressure compensation scheme, but also by the geometry of the toolpaths.
In order to separate these effects we report on the total print time when using back pressure compensation and when using a constant (maximum) movement speed in \cref{printtime}.
We estimate print times using a simulation of the Marlin firmware using the default movement settings of the setup described in \cref{print_results_section}.
While the idealized print time is predominantly determined by the total toolpath length, the print time using back pressure compensation is predominantly determined by the occurrence of wide beads, because they have a reduced the flow in \si{\milli\meter\cubed\per\second}.
Because of acceleration constraints imposed by the hardware the maximum movement speed is not reached near sharp corners.
We therefore also report on the angles of the bends in the toolpaths in \cref{smoothness}.
Furthermore, the print time is negatively affected by discontinuities in the extrusion process.
Between extrusions the printer needs to stop extrusion, travel to the next extrusion path and restart the extrusion process, which all take time.
For closed polygonal toolpaths we can start anywhere within the path, so we can optimize the starting location so as to minimize the travel time.
We therefore report both on the open and closed path count in \cref{pathcounts}.
}
